---
title: "hw3"
author: "Rohan Mishra ! github rohmish"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data(tips, package = "reshape2")
```

## Question 1
```{r}
partyCount = nrow(tips)
partyCount
```
there were 244 parties served.

## Question 2
```{r}
str(tips)
```

total_bill and tip are Numeric, size is an Integer, and sex, smoker, day, and time are all Factors.

## Question 3
```{r}
day = tips$day
day = day[order(match(day,  c("Thur","Fri","Sat","Sun")))]
day
```

## Question 4
```{r}
female5 = tips[(tips[,3] == "Female") & (tips[,7] >= 5), ]
female5
```

## Question 5
```{r}
library(ggplot2)
ggplot(tips, aes(x=total_bill, y=tip)) + geom_point() + xlab("Bill Amount") + ylab("Ammount of Tip")
```
There is a positive correlation between the total bill and tip.

## Question 6

1) 1 outlier is the bill amount of roughly $7 but the tip is at $5.

2) Once the bill gets decently high, the tio value is seen having a less positive correlation.

## Question 7
```{r}
tips$rateoftip = tips$tip/tips$total_bill
mean (tips$rateoftip)
```
On average, a waiter is tipped 16% of the total billthe average tip o a bill is about 16%
## Question 8
```{r}
ggplot(tips, aes(x = factor(tips$time, levels = c("Lunch","Dinner")), y = rateoftip)) + geom_boxplot() + xlab("Time") + ylab("Rate of Tip")
```
The average rate of tip is close to the same with a couple of outiers in dinner and the upper quartile of lunch being a bit larger.

## Question 9
```{r}
sexsmoker = tips
sexsmoker$new = paste(tips$sex,tips$smoker)
ggplot(sexsmoker, aes(x = total_bill, y = tip, color = new)) + geom_point() + xlab("Bill Amount") + ylab("Amount of Tip")
```

Males and Smokers tend to pay the highest tips

## Question 10
```{r}
ggplot(tips, aes(x = factor(day, levels = c("Thur","Fri","Sat","Sun")), fill=sex)) + geom_bar() +
xlab("Day of the Week") + ylab("Customers")
```

On weekends, you see more males than females. And on weekdays, it varies and you may find more females than men.